---
title: "Section 9"
output: pdf_document
---
##Exercises for section 9.1,9.2,9.3, and 9.6

####9.1
#####9.1.0.0.1
a%%b = divide a by b and give the remainder  
a%/%b= give the number of times b can be multiplied into a (division without taking into account remainder)

#####9.1.1.0.1
If the length of the longer is not a multiple of the shorter, R will give an error message and not complete the calculation

#####9.1.2.0.1
```{r}
v<-seq(1,13,4)
v
v<-seq(1,5,0.2)
v
```

#####9.1.2.0.2
When to is less than from, the sequence will count down at the increments specified using by.
```{r}
v<-(3:1)
v
```

#####9.1.3.0.1
```{r}
z<-c(1,3,5,7,9,11)
z
v<-z[seq(1,5,2)]
v
```
Using seq(1,5,2) produces a vector with numbers 1,3,5.  
Indexing vector z by this sequence gives the 1st (1), third (5), and fifth (9) values in the z vector

#####9.1.3.0.2
```{r}
v<-z[c(2,1,3)]
v
```

#####9.1.3.0.3
```{r}
z[9]<-11
z
```
This sets the value of the undefined element as the value specified and fills in all the values between the last defined element and the new element with NA

#####9.1.3.0.4
```{r}
x<-1:10
CalcY<-function(x){
  y=(x-1)/(x+1)
}
for (i in x){
  y<-c(CalcY(x))
}
plot(x,y)
lines(x,y)
```


#####9.1.3.0.5
In the third case, x rounded to 7 decimal places was once again 2.  
When subtracting in the 3rd case, the scientific notation becomes smaller than e-15 so the value is rounded.

#####9.1.3.0.6
```{r}
G<-c(0.5^seq(1,10))
SumDiffF<-sum(G)-(1/(1-0.5))
SumDiffF
H<-c(0.5^seq(1,50))
SumDiffH<-sum(H)-(1/(1-0.5))
SumDiffH
```


#####9.1.5.0.1
```{r}
Light <- c(20,20,20,20,21,24,44,60,90,94,101)
rmax <- c(1.73,1.65,2.02,1.89,2.61,1.36,2.37,2.08,2.69,2.32,3.67)
lowLight <- Light[Light<50]
lowLightrmax <- rmax[Light<50]
```
Replacing the name lowLight for Light would re-write the Light vector to only include values under 50.  
This would be the wrong thing to do because it would yield a new Light vector

#####9.1.5.0.2
```{r}
w<-runif(20)
wFltrd<-w[w < mean(w)]
wFltrd
```

#####9.1.5.0.3
```{r}
Pos<-which(w < mean(w))
Pos
```

#####9.1.5.0.4
```{r}
x[c(seq(1,length(x),3))]
x[c(TRUE, FALSE)]
```

####9.2
#####9.2.1.0.1
```{r}
v<-c(1,2)
x <- matrix(v,nrow = 2, ncol = 4)
x
```

#####9.2.1.0.1
```{r}
x<-matrix(rnorm(35),nrow = 5, ncol = 7)
```

#####9.2.2.0.1
```{r}
C <- cbind(1:3,4:6,5:7)
D <- rbind(1:3,4:6)
rbind(C,D)
cbind(C,C)
cbind(C,D)
```
rbinding the 2 matrices works because they have the same number of columns but cbinding the 2 matrices won't work because they have a different number of rows

####9.3
#####9.3.0.0.1
```{r}
x <- seq(1,27)
dim(x) <- c(3,9)
is.array(x)
is.matrix(x)
```
The vector has been assigned the dimensions following c(... . It is now a 2D array which is a matrix 

####9.6
#####9.6.0.0.1
```{r}
HurricaneDF<-read.csv("http://kingaa.github.io/R_Tutorial/hurricanes.csv",comment.char='#')
str(HurricaneDF)
```

